Why shouldn't you use numerical tests to diagnose the linear regression models?

### 2022-07-07 paper_comparison/paper_comparison/paper_comparison.Rmd
resolve citation

In addition to diagnostic plots, analysts may perform formal hypothesis testing for detecting model defects. Depends on the alternative hypothesis that being focused on, variety of tests can be applied. For example, the presence of heteroskedasticity can usually be tested by applying the White test [@white_heteroskedasticity-consistent_1980] or the Breusch-Pagan test [@breusch_simple_1979], which both derived from the Lagrange multiplier test (ref here) principle and rely on the asymptotic properties of the null distribution. For testing non-linearity, one may apply the F-test (ref here) to examine the significance of certain polynomial and non-linear forms of the regressors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [@ramsey_tests_1969].

@@

It was surprising that the essential components of visual inference had actually been established in @buja_inference_1999, but it was not until 10 years later that @buja_statistical_2009 formalized it as an inferential framework to extend confirmatory statistics to visual discoveries. This framework redefines the test statistics, tests, null distribution, significance levels and $p$-value for visual discovery modelled on the confirmatory statistical testing. Figure \@ref(fig:parallelism) outlines the parallelism between conventional tests and visual discovery.

![(ref:parallelism) \label{fig:parallelism}](figures/rsta2009012001.jpg){width=450 height=341}

(ref:parallelism) Parallelism between multiple quantitative testing and visual discovery [@buja_statistical_2009]. Visible features in a plot are viewed as a collection of test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)$, and any visual discoveries that are inconsistent with the null hypothesis are treated as evidence against the null. For regression diagnostics, the null hypothesis would be the assumed model, and visual discoveries could be any visual features in favour of any alternatives.

>>>>

In addition to diagnostic plots, analysts may perform formal hypothesis testing for detecting model defects. Depends on the alternative hypothesis that being focused on, variety of tests can be applied. For example, the presence of heteroskedasticity can usually be tested by applying the White test [@white_heteroskedasticity-consistent_1980] or the Breusch-Pagan test [@breusch_simple_1979], which both derived from the Lagrange multiplier test [@silvey1959lagrangian] principle and rely on the asymptotic properties of the null distribution. For testing non-linearity, one may apply the F-test to examine the significance of certain polynomial and non-linear forms of the regressors, or the significance of proxy variables as in the Ramsey Regression Equation Specification Error Test (RESET) [@ramsey_tests_1969].

@@

It was surprising that the essential components of visual inference had actually been established in @buja_inference_1999, but it was not until 10 years later that @buja_statistical_2009 formalized it as an inferential framework to extend confirmatory statistics to visual discoveries. This framework redefines the test statistics, tests, null distribution, significance levels and $p$-value for visual discovery modelled on the confirmatory statistical testing. Figure \ref{fig:parallelism} outlines the parallelism between conventional tests and visual discovery.

![Parallelism between multiple quantitative testing and visual discovery [@buja_statistical_2009]. Visible features in a plot are viewed as a collection of test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)$, and any visual discoveries that are inconsistent with the null hypothesis are treated as evidence against the null. For regression diagnostics, the null hypothesis would be the assumed model, and visual discoveries could be any visual features in favour of any alternatives. \label{fig:parallelism}](figures/rsta2009012001.jpg){width=450 height=341}

### 2022-07-07 paper_comparison/paper_comparison/paper_comparison.tex
resolve citation

In addition to diagnostic plots, analysts may perform formal hypothesis
testing for detecting model defects. Depends on the alternative
hypothesis that being focused on, variety of tests can be applied. For
example, the presence of heteroskedasticity can usually be tested by
applying the White test \citep{white_heteroskedasticity-consistent_1980}
or the Breusch-Pagan test \citep{breusch_simple_1979}, which both
derived from the Lagrange multiplier test (ref here) principle and rely
on the asymptotic properties of the null distribution. For testing
non-linearity, one may apply the F-test (ref here) to examine the
significance of certain polynomial and non-linear forms of the
regressors, or the significance of proxy variables as in the Ramsey
Regression Equation Specification Error Test (RESET)
\citep{ramsey_tests_1969}.

@@

It was surprising that the essential components of visual inference had
actually been established in \citet{buja_inference_1999}, but it was not
until 10 years later that \citet{buja_statistical_2009} formalized it as
an inferential framework to extend confirmatory statistics to visual
discoveries. This framework redefines the test statistics, tests, null
distribution, significance levels and \(p\)-value for visual discovery
modelled on the confirmatory statistical testing. Figure
@ref(fig:parallelism) outlines the parallelism between conventional
tests and visual discovery.

\begin{figure}
\centering
\includegraphics[width=4.6875in,height=3.55208in]{figures/rsta2009012001.jpg}
\caption{(ref:parallelism) \label{fig:parallelism}}
\end{figure}

(ref:parallelism) Parallelism between multiple quantitative testing and
visual discovery \citep{buja_statistical_2009}. Visible features in a
plot are viewed as a collection of test statistics
\(T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)\), and any visual
discoveries that are inconsistent with the null hypothesis are treated
as evidence against the null. For regression diagnostics, the null
hypothesis would be the assumed model, and visual discoveries could be
any visual features in favour of any alternatives.

>>>>

In addition to diagnostic plots, analysts may perform formal hypothesis
testing for detecting model defects. Depends on the alternative
hypothesis that being focused on, variety of tests can be applied. For
example, the presence of heteroskedasticity can usually be tested by
applying the White test \citep{white_heteroskedasticity-consistent_1980}
or the Breusch-Pagan test \citep{breusch_simple_1979}, which both
derived from the Lagrange multiplier test \citep{silvey1959lagrangian}
principle and rely on the asymptotic properties of the null
distribution. For testing non-linearity, one may apply the F-test to
examine the significance of certain polynomial and non-linear forms of
the regressors, or the significance of proxy variables as in the Ramsey
Regression Equation Specification Error Test (RESET)
\citep{ramsey_tests_1969}.

@@

It was surprising that the essential components of visual inference had
actually been established in \citet{buja_inference_1999}, but it was not
until 10 years later that \citet{buja_statistical_2009} formalized it as
an inferential framework to extend confirmatory statistics to visual
discoveries. This framework redefines the test statistics, tests, null
distribution, significance levels and \(p\)-value for visual discovery
modelled on the confirmatory statistical testing. Figure
\ref{fig:parallelism} outlines the parallelism between conventional
tests and visual discovery.

\begin{figure}
\centering
\includegraphics[width=4.6875in,height=3.55208in]{figures/rsta2009012001.jpg}
\caption{Parallelism between multiple quantitative testing and visual
discovery \citep{buja_statistical_2009}. Visible features in a plot are
viewed as a collection of test statistics
\(T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)\), and any visual
discoveries that are inconsistent with the null hypothesis are treated
as evidence against the null. For regression diagnostics, the null
hypothesis would be the assumed model, and visual discoveries could be
any visual features in favour of any alternatives.
\label{fig:parallelism}}
\end{figure}
